Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-08 SIR_manuscript.tex
new representation of Delta, diff Delta wrt rho is quadratic

The particular form of $F$ with two rows of zeros at the bottom, simplifies $G$ as the following block matrix.
\begin{equation}
\label{mat:G}
G = \left[ \begin {array}{cc}
G_{11}&G_{12}\\
0&0
\end {array} \right],
\end{equation}
where the 2 by 2 submatrix $G_{11}$ is 
\begin{equation}
\label{G11}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  x\_n^* \\ x\_u^* \\ 0 \\ 0  \end {array} \right]
\left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right]
\left[ \begin {array}{cc}
\gamma(\omega+\gamma)^2 & \gamma\omega(\omega+\gamma)\\ \noalign{\medskip}
\gamma(\omega+\gamma)(1-p_I)F_I & \gamma(\omega+\gamma)(F_I+\gamma) \\ \noalign{\medskip}
\gamma(\omega+\gamma) p_I F_I & \gamma\omega p_I F_I \\ \noalign{\medskip}
\omega(\omega+\gamma) p_I F_I & \omega^2 p_I F_I
\end {array} \right].
\end{equation}

@@

It remains hard to show the reduction of $\Rnum$ with respect to \percap testing intensity, $\rho$, and the speed of the test return, $\omega$, for the feasible ranges of the parameters, i.e., $0<\omega$, $0 \leq \rho<\omega$, and $0 \leq \theta\_w \leq \theta\_c \leq 1$. One easy way to do such an analysis is based on the fact that $\rho$ is \percap rate so for a large population size, $N_0 \gg 1$, $\rho$ is very small or close to 0, comparing to $N_0$. This provides a base to linearly approximate $\Rnum$ when $\rho$ is close to 0, and use this approximation to analyze the behaviour of $\Rnum$ with respect to $\omega$ (see section \ref{taylor}). In the next section we provide an equivalent representation of $\Rnum$ for our model to provide to follow proving that more testing intensity decreases $\Rnum$ for a general rane of parameters.

@@

>>>>

The particular form of $F$ with two rows of zeros at the bottom, simplifies $G$ as the following block matrix.
\begin{equation}
\label{mat:G}
G = \left[ \begin {array}{cc}
G_{11}&G_{12}\\
0&0
\end {array} \right],
\end{equation}
where the 2 by 2 submatrix $G_{11}$ is 
\begin{equation}
\label{G11}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  x\_n^* \\ x\_u^*  \end {array} \right]
\left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right]
\left[ \begin {array}{cc}
\gamma(\omega+\gamma)^2 & \gamma\omega(\omega+\gamma)\\ \noalign{\medskip}
\gamma(\omega+\gamma)(1-p_I)F_I & \gamma(\omega+\gamma)(F_I+\gamma) \\ \noalign{\medskip}
\gamma(\omega+\gamma) p_I F_I & \gamma\omega p_I F_I \\ \noalign{\medskip}
\omega(\omega+\gamma) p_I F_I & \omega^2 p_I F_I
\end {array} \right].
\end{equation}

@@

It remains hard to show the reduction of $\Rnum$ with respect to \percap testing intensity, $\rho$, and the speed of the test return, $\omega$, for the feasible ranges of the parameters, i.e., $\omega>0$, $0 \leq \rho<\omega$, $0 \leq \theta\_w \leq \theta\_c \leq 1$ and $\frac{w_I}{w_S}\geq 1$. One easy way to do such an analysis is based on the fact that $\rho$ is \percap rate so for a large population size, $N_0 \gg 1$, $\rho$ is very small or close to 0, comparing to $N_0$. This provides a base to linearly approximate $\Rnum$ when $\rho$ is close to 0, and use this approximation to analyze the behaviour of $\Rnum$ with respect to $\omega$ (see section \ref{taylor}). In the next section we provide an equivalent representation of $\Rnum$ for our model to provide to follow proving that more testing intensity decreases $\Rnum$ for a general rane of parameters.

@@

Another representation of matrix $G_{11}$ in \eqref{G11} is as follows.
\begin{equation}
\label{G112}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  x\_n^* \\ x\_u^*  \end {array} \right]
\left[ \begin {array}{cccc} 
C-C_1, C-C_1-C_2\end {array} \right],
\end{equation}
where $C$ is in Eq. \eqref{eq:abc}, and $C_1$ and $C_2$ are 
\begin{align}
\label{eq:C12}
C =& (\omega+\gamma)(\gamma(\omega+\gamma)+(\omega\,p_I+\gamma)\,F_I)\\
C_1 =& (\omega+\gamma)(\theta\_w \, \gamma+\theta\_c\, \omega\, p_I) F_I,\\
C_2 =& (\omega+\gamma)\gamma^2\,\theta\_w+(\theta\_w-\theta\_c)\gamma\,p_I\,F_I.
\end{align}
$\Rnum$ is in the same form as in Eq. \eqref{R0}  $$\Rnum= \frac{\beta}{\gamma} (1-\Delta),$$
with equivalent but simplified $\Delta$ as
\begin{equation}
\label{eq:del2}
\Delta= \frac{C_1+C_2\,x\_n^*}{C}.
\end{equation}
The behavior of $\Rnum$ with respect to $\rho$ is determine by $\pro \Delta$
\begin{align}
\label{eq:dd2dr}
\pro \Delta=& \frac{1}{d} (a\,\rho^2+b\,\rho+c), \text{where}\\
a=& ((\omega+\gamma)\gamma -\omega \frac{w_I}{w_S} (\omega\,p_I+\gamma)) D_1,\\
b=& -2\gamma\omega(\omega+\gamma) D_1,\\
c=& \omega^2 (\omega+\gamma)^2 D_2,
\end{align}
with scaler $d>0$ (not effecting the sign of $\pro \Delta$) and $D_1$ and $D_2$ as 
\begin{align}
\label{eq:D1D2}
D_1=& (\omega+\gamma)\gamma\theta\_w+(\theta\_c-\theta\_w)\omega^2\,p_I\,\frac{w_I}{w_S}, \\
D_2=& (\omega\,\frac{w_I}{w_S}+\gamma)\gamma\theta\_w+\omega^2\,p_I\,\frac{w_I}{w_S}\,\theta\_c.
\end{align}
